- Abstract (NO/ENG)
- Contents
- Figures
- Tables
- Code Listings
- Acronyms (legg til i glossary.tex) HVORDAN VISE I F DOKUMENTET?!?
- Acknowledgements

1. Introduction (6-8)
 - Background: about Mobai (1/2)
 - Scope: subject area, delimitation, task description (1-2)
 - target groups (1/4)
    * users of the web application
    * Thesis reader
 - Why did we choose this task? (1)
 - The team (1-2)
   - Who we are / the team members (1/2)
   - Academic backgrounds (1/2)
   - Roles (1/2)
   - Decision making
 - Structure of the report (1)
 
 2. Specification (4-5)
    - Choice of development method (2-3) 
        - considered models (1)
    - Risk analysis
    
    
3. Face Quality Assessment (6-7)
    - What is a good image (Quality) (2-3)
    - About Face quality metrics (3)
        - ISO (1)
        - FaceQNet (1)
  
  
4. Objective assessment (15-20)
    - Application requirements (4-5)
        * Use cases (3)
        * Misuse cases (1-2)
    - Why have we chosen web (react) + python (flask)? (1-2). docker(containerization) 
    - explain frontend (react, material-ui) (1)
    - explain backend (axios) (restAPI) (1)
    - explain why we use containerization (docker) (1)
    - Implementation (2)
        * How they all work together
    - Testing: unit testing, user testing (1-2)
    - Results (1)
    

5. Subjective experiment (16-20)
   - Conducting the survey  (6-7)
        * Factors (1) 
        * Our choice (1-2) 
        * Corona disadvantages (1/2)
        * Introduction manual (2) 
        * Type of people/participants (1/2)
        * What went wrong (1)
    - Datasets (6-9)
        * Combined passport alike (1)
            - Cameras used
        * Capture from photo ntnu dataset (1/2)
        * Selfie dataset (1/2)
        * Combining datasets (2)
        * Creating our own dataset (3-4)
            - Masker/ munnbind 
            - Tilting 
    - Results(3) 
        * Overall (3/2)
        * Mobai (1/2)
        * Normal people (non-experts)(1/2)
        * Correlation between Mobai and normal people(1)
            - The tools
 
6. Results (3)
     - discuss correlation between subj/obj. assessment (3)
  
7. Conclusion (4)
    - Object assessment evaluation
    - Subjective assessment evaluation
    - Group work evaluation
    - can the two FIQMs be used further? (2)
    - how are the objective similar to the subjective? same quality scores? (2)
  
 Appendix
x    - Project plan
x    - Survey instructions
x    - Project agreements with NTNU (and Mobai?)
x    - Summary meeting reports with supervisor
x    - Summary meeting reports with Mobai
    - Toggl report
    - Results raw data. As CSV or Excel?
    
 
 ----
Sjekk før innlevering:
- Alle Comments er "resolved"
- Alle captions i figurer og tabeller har/ikke punktum til slutt
- Alle paragrafinnrykk er riktig.
- "facial images", "face image quality"
- "Code listing", "Table", "Figure" er skrevet likt.
- "Python", "Dockerfile", "Docker", "Flask", "Django" osv er skrevet likt.
- "FaceQnet", "ISO Metrics"
- Kildelisten ser riktig ut.
- Fjern upassende white space.
- Skal vi ha quotes rundt navnene på datasettene?
- Noen av bildene har (a) og (b) under seg. Andre ikke.
- Heading oppe i høyre hjørne (navnet på rapporten) må være i orden
- Det må nødvendigvis ikke være blank side mellom hvert kapittel (https://tex.stackexchange.com/questions/180722/per-chapter-blank-page-disappears-after-chapter-2)
 
 ----
 Mellomrom mellom tekst og citation
 Parenteser rundt figurnavn eller ikke?
 
 Photoshop: 
 Compression: Level 1
 Blur: 2
 Noise: 7 \%
 
%The three image lineups in Figure \ref{fig:ICAOlineup} showcases typical flaws of facial images that negatively affect the quality. The last image of each lineup is considered to have the best quality. The flaws described varies in severity. The face image quality of the lady with her face covered would be at the bottom of the quality scale. The first two images of the man, would not affect the quality to the same degree and the quality of the first two images of the kid, would affect the quality even less. 
 
Julian er kuuuul
                                       /;    ;\
                                  __  \\____//
                                 /{_\_/   `'\____
                                 \___   (o)  (o  }
      _____________________________/          :--'
  ,-,'`@@@@@@@@       @@@@@@         \_    `__\
 ;:(  @@@@@@@@@        @@@             \___(o'o)
 :: )  @@@@          @@@@@@        ,'@@(  `===='
 :: : @@@@@:          @@@@         `@@@:
 :: \  @@@@@:       @@@@@@@)    (  '@@@'
 ;; /\      /`,    @@@@@@@@@\   :@@@@@)
 ::/  )    {_----------------:  :~`,~~;
;;'`; :   )                  :  / `; ;
;;;; : :   ;                  :  ;  ; :
`'`' / :  :                   :  :  : :
   )_ \__;      ";"          :_ ;  \_\       `,','
   :__\  \    * `,'*         \  \  :  \   *  8`;'*
       `^'     \ :/           `^'  `-^-'   \v/ :
       
