%\dominitoc% Initialization
%\tableofcontents
\chapter{Meetings With Project Supervisor}
\label{appendix:supervisor}

We had regular meetings with our project supervisor Ali on Mondays at 12:00. There were also some extraordinary meetings during the project.

% TODO: add the latest meeting reports, after the 10th of May.

\section*{Meeting with project supervisor 11.01.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Getting started.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item Think about how we will run the user tests?
    \item Where will we get face images? From Mobai?
    \item About the project report: potential for a publication?
\end{itemize}

\subsection*{Agenda for the next week}
\begin{itemize}
    \item Prepare a time plan.
    \item Should we write everything in English?
\end{itemize}



\section*{Meeting with project supervisor 18.01.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Explain the project further to the supervisor.
    \item Show the time plan to the supervisor.
        \begin{itemize}
            \item The subjective experiment will take more than a month. Probably one and a half months.
    \end{itemize}
    \item Discuss further work
    \begin{itemize}
        \item The final product: local application or web application?
        \item Time requirements for the subjective assessment (manual observations). How long will it take? Probably many weeks.
    \end{itemize}
    \item Show and discuss the group rules.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item How should we conduct the subjective experiment?
    \begin{itemize}
        \item Evaluate which platform we want to use and why we decide to use it. We can use QuickEval, SurveyMonkey, LimeSurvey, or some other platform.
        \item The images should be shown in a random order.
        \item What can we include in our dataset/subjective experiments that are unique?
    \end{itemize}
    \item Create a structure of the thesis, with names of the chapters and sections. Include the number of pages. 
\end{itemize}

\subsection*{Agenda for the next week}
\begin{itemize}
    \item Send research papers and group rules to Ali.
    \item Write the first draft for the structure of the thesis. Write down the chapter names and number of pages.
\end{itemize}



\section*{Meeting with project supervisor 27.01.2021}
\subsection*{Planned agenda}
\begin{itemize}
\item Show our project plan
\item Show our draft of the project structure with chapter headings and number of pages.
\item Subjective assessment: 
    \begin{itemize}
    \item Which score range is the best one to use? 1-5, 1-20?
    \item How should we do the survey? Score one and one image? Put multiple images in order of quality score?
    \end{itemize}
\item In the report, can we use different tenses (past, present, future) in the same paragraph?
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item Draft of the project structure:
    \begin{itemize}
        \item Add numbers to the chapters.
        \item Add the number of pages (and required time) to sections.
        \item The sections we have written down look good.
        \item Maybe move the subjective assessment to a separate chapter (if it’s long and makes sense to put it in a separate section). 
        \item Excessive theory that is not used in the report will affect the grading of the report.
    \end{itemize}
    \item Creating the subjective assessment:
    \begin{itemize}
        \item Check a few datasets that are out there, see what they do and how they do it.
        \item Display the images in random order.
    \end{itemize}
    \item About the thesis writing.
    \begin{itemize}
        \item Don’t jump between tenses. Use Past tense.
        \item In the results, use past or present tense.
        \item Do a shift to present in the end.
        \end{itemize}
\end{itemize}

\subsection*{Agenda for the next week}
\begin{itemize}
    \item Send the project plan to Ali.
    \item Look into one or two data sets.
    \item Finalize our time plan.
\end{itemize}



\section*{Meeting with project supervisor 01.02.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Go through our project plan and the comments from Ali.
    \item Show the supplementary agreement from Mobai. Any thoughts?
    \item What is a data set? A collection of images?
    \item Our goal with the application. How should it work?
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item We went through the project plan and wrote down the comments from Ali.
    \item Speak to Tom about the supplementary agreement.
    \item Speak with Mobai about how the application should work. 
    \item Dataset:
    \begin{itemize}
        \item It’s called a dataset or datasets (one word). \item Dataset: a collection of images.
        \item We evaluate the quality of an image.
        \item The quality of the dataset: how we present and run the test decides the quality of the dataset. The higher the quality, the more reliability.
    \end{itemize}
\end{itemize}

\subsection*{Agenda for the next week}
\begin{itemize}
    \item Create a pilot test for the subjective experiment. Be prepared for comments and changes. Have a finished test by the 15th of February.
\end{itemize}



\section*{Meeting with project supervisor 08.02.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Show our pilot of the subjective experiment.
    \item Mobai’s and Ali’s definition of a quality image are two different things? 
    \item We will use SurveyMonkey/QuickEval for the subjective experiment, with random image order. 
    \item Our dataset consists of 280 images. Mobai wants all participants in the subjective experiment to rate all of the 280 images in the dataset.
    \item How do we perform the subjective experiment?
    \item How do we pick the best 100 images from the “Faces in the wild” dataset?
    \item Invite Ali to join a meeting with Mobai.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item Use the same rating system for the experiment.
    \item Can we split the images in the subjective experiment into three sets? Ask Mobai.
    \item How do we perform the subjective experiment?
    \begin{itemize}
        \item Suggestion for the subjective experiment: split the experiment into 3 sessions. One session for each image folder in the dataset. Should the sessions be split over multiple days or the same day with breaks between sessions?
        \item Remember: if we split into multiple sessions we need to track the sessions of the participants so we can connect the different sessions to the same participant.
        \item Have a training set first to train the participants for the experiment?
        \item Don’t mention “quality” (or, define clearly what we mean by quality.
        \item We want to test the face recognition quality.
        \item Define who we want to ask to take the subjective experiment.
    \end{itemize}
    \item How do we pick the best 100 images from the “Faces in the wild” dataset?
    \begin{itemize}
        \item Variant image quality matters. I.e., pick a variety of images where the faces are covered or less visible in some way, e.g. with sunglasses, different poses, different perspectives and so on.
        \item Also pick images where the faces are clearly visible (“passport-like”).
    \end{itemize}
    \item There are three kinds of metrics:
    \begin{itemize}
        \item Full access metrics
        \item Reduced reference
        \item No reference
    \end{itemize}
    \item Ali will join our next meeting with Mobai on Tuesday.
\end{itemize}

\subsection*{Agenda for the next week}
\begin{itemize}
    \item Create clear instructions for the users of the subjective experiment. What do we want the users to evaluate? 
    \item Test the datasets with the IQMs and check out the results.
\end{itemize}



\section*{Meeting with project supervisor 11.02.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Talk about our meeting with Mobai on Tuesday.
    \item Use face image quality score from 1-10?
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item Find the smallest of all of the images in the datasets. Downsize all the images to the same size (and keep the aspect ratio).
    \item Use the  face image quality scores 1-5, or maybe 1-7?
\end{itemize}



\section*{Meeting with project supervisor 15.02.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Go through the comments on the survey instructions
    \item Should all of the images be of the same size?
    \item Dataset 3, “Faces in the wild” is not good enough.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item We went through the survey instructions and made the necessary adjustments:
    \begin{itemize}
        \item We can create a control dataset. We can use images of ourselves.
        \item We will create image lineups from the control dataset.
        \item Have Mobai rate the images in the survey instruction.
    \end{itemize}
\end{itemize}



\section*{Meeting with project supervisor 22.02.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Update on our current status:
    \begin{itemize}
        \item Currently working on the frontend and backend for the web application.
    \end{itemize}
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item We will continue working on the web application.
\end{itemize}



\section*{Meeting with project supervisor 01.03.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Show experiment instructions:
    \begin{itemize}
        \item At the beginning of the instructions, include “a very brief intro about the face recognition system”?
        \item Delete the slides at the end?
    \end{itemize}
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item Survey instructions:
    \begin{itemize}
        \item Send 15 images each to Mobai and have them rate all of them. Ask Guoqiang to have them rated by Wednesday.
        \item In the image lineups: image with the lowest score on the left.
        \item Random is good. In a lineup, we include different pictures of each of the members. Have a 1-5 rating for each member.
    \end{itemize}
    \item Write about our dataset in the thesis.
    \item Before sending out the subjective experiment:
    \begin{itemize}
        \item Test the experiment ourselves first.
        \item Get approval of the experiment by sending it to Ali and Guoqiang.
        \item Then send it out to a few people, not all of them.
    \end{itemize}
    \item Start writing about things in the thesis that will not change.
\end{itemize}

\subsection*{Agenda for the next week}
\begin{itemize}
    \item Send 15 images each to Mobai and have them rate all of them. Ask Guoqiang to have them rated by Wednesday.
    \item Ask mobai if they want us to create our own dataset.
\end{itemize}



\section*{Meeting with project supervisor 08.03.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item About the subjective experiment on QuickEval.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item About sending out the subjective experiment to the participants:
    \begin{itemize}
        \item Do not ask the users for any personal information in the survey.
        \item Add “Mobai” in the title of the email. The title of the email is important. We need to engage people.
        \item Use Blind carbon copy (BCC) when sending the email to survey participants.
    \end{itemize}
\end{itemize}

\subsection*{Agenda for the next week}
\begin{itemize}
    \item Send the mail to Ali and Guoqiang first.
    \item Send the mail to the participants.
\end{itemize}



\section*{Meeting with project supervisor 15.03.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item About the dataset we are creating. How do we create a “wow factor”?
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item Suggestions for the dataset we are creating:
    \begin{itemize}
        \item Make it a bit challenging. 
        \item Have other people in the background. 
        \item Painting of someone in the background.
        \item Partial faces (like the selfie dataset).
        \item Test images with the metrics.
    \end{itemize}
    \item We discussed different ways to display the data from the experiments:
    \begin{itemize}
        \item Calculate the different correlation values. Which metric is performing better?
        \item 3D-plot, Spider chart, Rose chart.
        \item How we present it is important. It will stick in the mind of the reviewer. 
        \item What do we want to present to the user?
    \end{itemize}
\end{itemize}



\section*{Meeting with project supervisor 22.03.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Is Ali gone next Monday?
    \item Delimitation (avgrensning?)
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item There will be a meeting next Monday as usual.
    \item We talked about the structure of the thesis:
    \begin{itemize}
        \item Why we made the decisions we did.
        \item Write about why we went for a web platform. Pros and cons.
        \item Write the skeleton for the whole thesis.
        \item Write the sections so we easily can move them around.
        \item Add flow between the sections.
    \end{itemize}
\end{itemize}



\section*{Meeting with project supervisor 29.03.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Thesis structure.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item We discussed how we should structure the thesis (details not included).
\end{itemize}

\subsection*{Agenda for the next week}
\begin{itemize}
    \item Send thesis chapter 1 to Ali.
\end{itemize}



\section*{Meeting with project supervisor 06.04.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Talk about the thesis.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item Ali will look at the final draft of our chapters: 
    \begin{itemize}
        \item Send him the final draft of a chapter when we finish it. 
        \item He will go through the whole report in the end.
    \end{itemize}
    \item Some other people will join our meeting on the 19th.
    \item Find a name for our dataset.
\end{itemize}



\section*{Meeting with project supervisor 12.04.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Review thesis chapter 1.
    \item Will Ali join our meeting with Mobai tomorrow?
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item We reviewed chapter 1:
    \begin{itemize}
        \item Be more strict about using paragraphs. The language is good, just present it in a better way.
    \end{itemize}
    \item Run the matrices on our own dataset. 
\end{itemize}



\section*{Meeting with project supervisor 19.04.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Discuss thesis chapter 2.
    \item Creating our own dataset is completed.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item We discussed thesis chapter 2 and the comments from Ali. (Comments are not added).
    \item We will create a second subjective experiment with our own dataset:
    \begin{itemize}
        \item Select 250 images from the dataset.
        \item Add effects like blurring, noise etc. to the images and test them with the metrics. Will the scores change?
    \end{itemize}
\end{itemize}



\section*{Meeting with project supervisor 26.04.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Discuss user testing.
    \item Split the second subjective experiment into two parts? 125 images in each part.
    \item Can Ali edit 50 of the images? How should we edit the images? Blurring, noise, exposure.
    \item Talk about the results from the subjective experiment.
    \item Plotting the results from the experiments.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item User tests should be done by people at Mobai.
    \item We discussed the second subjective experiment. 
    \item We will create a third subjective experiment based on the second subjective experiment:
    \begin{itemize}
        \item Select 50 images from the second subjective experiment. 10 images from each rating category (10 images rated 1 - poor, 10 images rated 2 - bad, and so on).
        \item Edit the images in different ways and create the new experiment with these images.
        \item We can add “untypical” distortions.
    \end{itemize}
    \item We talked about the thesis and the metrics. (Notes not included).
    \item Plotting the results:
    \begin{itemize}
        \item Box plot. Shows the distribution of the scores.
        \item Show experts, non-experts, and both of them together.
        \item Subjective and objective scores should be separate.
    \end{itemize}
    \item Our dataset:
    \begin{itemize}
        \item All images in the dataset should be portrait. Fix landscape images to portrait images. 
    \end{itemize}
\end{itemize}



\section*{Meeting with project supervisor 03.05.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item All invited participants have completed the second subjective experiment.
    \item How should we distort the images for the final experiment?
    \item Discuss thesis chapter 3.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item We discussed thesis chapter 3. (Notes not included).
    \item Create the third and final subjective experiment:
    \begin{itemize}
        \item Select 50 images, 10 images from each rating category.
        \item The image should be as diverse as possible.
        \item Add four distortions to each image:
        \begin{itemize}
            \item Two types of compression, e.g., Facebook Messenger.
            \item Two types of image edits, e.g., noise, blur or exposure.
            \item The distortions should be reproducible, i.e., something that other people can do. Use e.g., Photoshop or IrfanView.
        \end{itemize}
    \item Include the unedited version of the images.
    \item Summary: 200 (50 x 4) distorted + 50 non-distorted. In total, 250 images.
    \item Use these 250 images and create the final experiment.
    \end{itemize}
\end{itemize}


\section*{Meeting with project supervisor 06.05.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Talk about the third subjective experiment.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item We discussed the third subjective experiment:
    \begin{itemize}
        \item The dataset should be challenging for the metrics.
        \item The changes should not change the subjective scores.
        \item Use Telegram compression. Telegram changes the images.
        \item The editing we have done is too dramatic. Tune it down.
        \item When we add noise or blur to the images, find a value that works for about 30-35 of the images.
    \end{itemize}
\end{itemize}


\section*{Meeting with project supervisor 10.05.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Discuss the thesis and the future bachelor presentation.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item We discussed finishing the thesis.
    \item We talked about the future bachelor presentation.
    \item Send the chapters we discussed to Ali by Thursday.
    \item We will have a meeting Friday afternoon the 14th of May.
    \item We will have a meeting on Tuesday at 11:00 the 18th of May.
\end{itemize}


\section*{Meeting with project supervisor 14.05.2021}

\subsection*{Planned agenda}
\begin{itemize}
    \item Discuss chapter 4 of the thesis.
    \item Discuss chapter 5 of the thesis.
    \item Discuss the conclusion of the thesis.
    \item Discuss the abstract.
    \item Should we keep the list of acronyms?
    \item Should we include a glossary?
    \item How do we properly include photo credits for the images used in the figures?
    \item Prepare a final schedule for the project.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item We will edit chapter 4 and 5, based on the feedback from Ali.
    \item We are currently finishing the work on chapters 6 and 7. We will send the draft to Ali.
    \item We will keep the list of acronyms.
    \item We will not include a glossary.
    \item We will send Ali our thesis on the 16th of May.
    \item We have prepared a final schedule for the project.
\end{itemize}


\section*{Meeting with project supervisor 18.05.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Discuss the feedback on the thesis.
    \item What to include as appendices?
    \item What is a fitting name for the thesis?
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item We will review the thesis based on the feedback from Ali.
    \item We will further discuss what to include in the appendices.
    \item "Face Image Quality Assessment" can be a fitting name for the thesis.
\end{itemize}


\section*{Meeting with project supervisor 19.05.2021}
\subsection*{Planned agenda}
\begin{itemize}
    \item Discuss our review of chapter 6.
    \item Discuss the abstract.
\end{itemize}

\subsection*{Summaries}
\begin{itemize}
    \item We will do some more changes to chapter 6.
    \item We will have a few meetings with Ali again before the project presentation.
\end{itemize}